\huge Microbial Interaction Database pipeline - Figures draft \#4

### 2019-04-23 figures.tex
Update figure 6(b) legend
Change: Update figures.tex for 4th draft and presentation

\title{ \huge Microbial Interaction Database pipeline - Figures draft \#2 }
\author{DK, GB, ZH, CD, KK, DS}
\date{\today}

@@

\begin{figure}[h]
  \centering
  \includegraphics[width=0.7\linewidth]{figure1.pdf}
  \caption{
    \textbf{The workflow of the microbial co-occurrence analysis pipeline}.
    The processes can be grouped into four major steps: \textbf{(A)} denoising and clustering, \textbf{(B)} taxonomy assignment, \textbf{(C)} OTU/ESV processing, and \textbf{(D)} network inference.
    Each step incorporates several processes, each of which in turn have several alternate algorithms for the same task (indicated by the text to the right of the blue boxes).
    \textbf{(E)} shows the average variances in the final networks contributed by each of the four groups over all the test datasets
  }
  \label{fig:main_figure}
\end{figure}

\begin{figure}[h]
  \centering
  \includegraphics[width=\linewidth]{figure2.pdf}
  \caption{
    \textbf{Comparison of representative sequences generated by the various denoising and clustering algorithms used in the workflow.}
    \textbf{(A)} The average weighted UniFrac distance between the representative sequences,
    \textbf{(B)} The average unweighted UniFrac distance,
    \textbf{(C)} The distributions of the average unweighted UniFrac distance between original sequence profile and calculated sequence profile in mock datasets (this will be replaced with a violoin plot)
  }
  \label{fig:figure2}
\end{figure}

\begin{figure}[h]
  \centering
  \includegraphics[width=\linewidth]{figure3.pdf}
  \caption{
    \textbf{Comparison of taxonomy assignments using different taxonomy reference databases}
    \textbf{(A)} Taxonomy composition of the 20 most abundant genera predicted using different taxonomy references databases: Greengenes, SILVA and NCBI.
    The legend shows the common and the unique genera among the taxonomy assignments.
    \textbf{(B)} The percentage of OTUs assigned to the same taxonomic label when using different reference databases.
    The percentage of matches are shown at various taxonomic levels.
    \textbf{(C)} The bray-curtis dissimilarity between the original taxonomy profile and calculated taxonomy profile in the mock datasets.
  }
  \label{fig:figure3}
\end{figure}

\begin{figure}[h]
  \centering
  \includegraphics[width=\linewidth]{figure4.pdf}
  \caption{
    \textbf{Networks generated using different network inference methods}.
    \textbf{(A)} The four different networks generated by different network inference methods are very dissimilar
    \textbf{(B)} The edge overlap upset plot
    \textbf{(C)} The node overlap upset plot.
  }
  \label{fig:figure4}
\end{figure}

\begin{figure}[h]
  \centering
  \includegraphics[width=\linewidth]{figure6.pdf}
  \caption{Example networks generated using our pipeline: Final consensus networks for some datasets}
  \label{fig:figure6}
\end{figure}

\begin{figure}[h]
  \centering
  \includegraphics[width=0.8\linewidth]{figure6.pdf}
  \caption{
    \textbf{The choice of database contributes to the most variance in the networks}.
    \textbf{(A)} The relative variance in the networks contributed by the denoising, taxonomy assignment and filtering steps.
    \textbf{(B)} The PCA plot clearly shows that the networks can be separated based on database
  }
  \label{fig:figure1}
\end{figure}

@@

@@

\begin{figure}[h]
  \centering
  \includegraphics[width=0.7\linewidth]{figures2.pdf}
  \caption{Effect of OTU processsing measures on the OTU table. This is just a placeholder}
  \label{fig:figures2}
\end{figure}

\begin{figure}[h]
  \centering
  \includegraphics[width=0.8\linewidth]{pdf/all_denoise_reg.pdf}
  \caption{All pairwise correlations comparing the similarity between different denoising and clustering methods}
  \label{fig:figures3}
\end{figure}

>>>>

\title{ \huge Microbial Interaction Database pipeline - Figures draft \#4 }
\author{DK, GB, ZH, CD, KK, DS}
\date{\today}

@@

\begin{figure}[h]
  \centering
  \includegraphics[width=0.67\linewidth]{figure1.pdf}
  \caption{
    \textbf{The workflow of the microbial co-occurrence analysis pipeline}.
    The processes can be grouped into four major steps: \textbf{(DC)} denoising and clustering, \textbf{(TA)} taxonomy assignment, \textbf{(OP)} OTU/ESV processing, and \textbf{(NI)} network inference.
    Each step incorporates several processes, each of which in turn have several alternate algorithms for the same task (indicated by the text to the right of the blue boxes).
  }
  \label{fig:figure1}
\end{figure}

\begin{figure}[h]
  \centering
  \includegraphics[width=0.75\linewidth]{figure2.pdf}
  \caption{
    \textbf{The choice of taxonomic reference database contributes to the most variance in the networks}.
    \textbf{(A)} The relative variance in the networks contributed by the denoising, taxonomy assignment and filtering steps.
    \textbf{(B)} The PCA plot shows that the networks can be clearly separated based on the database used for the taxonomy assignment
  }
  \label{fig:figure2}
\end{figure}

\begin{figure}[h]
  \centering
  \includegraphics[width=\linewidth]{figure3.pdf}
  \caption{
    \textbf{The representative sequences generated by the different denoising/clustering methods mostly differ in the sequences that are in low abundance.}
    \textbf{(A)} The average weighted UniFrac distance between the representative sequences shows that the representative sequences and their compositions are fairly identical between the methods,
    \textbf{(B)} The largers average unweighted UniFrac distance indicates that methods differ in their identifaction of sequences of low abundance,
    \textbf{(C)} The distributions of the average unweighted UniFrac distance between the expected sequence profile and the calculated sequence profile in mock datasets show that dada2 and deblur were the best performing methods in most of the datasets.
  }
  \label{fig:figure3}
\end{figure}

\begin{figure}[h]
  \centering
  \includegraphics[width=\linewidth]{figure4.pdf}
  \caption{
    \textbf{Taxonomic reference databases vary widely in terms of their taxonomies.}
    \textbf{(A)} The assignment of the top 50 representative sequences to their respective taxonomies using the three different reference databases shows how the same sequences are assigned to different genus.
    \textbf{(B)} The percentage of OTUs assigned to the same taxonomic label when using different reference databases.
    The percentage of mis-matches decrease at higher taxonomic levels but even at the Phylum level there exists around 10\% of mis-matches.
    \textbf{(C)} The bray-curtis dissimilarity between the expected taxonomy profile and calculated taxonomy profile in the mock datasets shows that there is no best choice of database for every dataset.
  }
  \label{fig:figure4}
\end{figure}

\begin{figure}[h]
  \centering
  \includegraphics[width=0.85\linewidth]{figure5.pdf}
  \caption{
    \textbf{Networks generated using different network inference methods show marked differences both in terms of edge-density and connectivity}.
    \textbf{(A)} The six different networks generated by the different network inference methods are very dissimilar
    \textbf{(B)} The node overlap upset plot indicates that all the networks have a large number of common nodes involved in connections.
    Whereas, \textbf{(C)} The edge overlap upset plot shows that a very small fraction of these connections are actually shared.
  }
  \label{fig:figure6}
\end{figure}

\begin{figure}[h]
  \centering
  \includegraphics[width=0.9\linewidth]{figure6.pdf}
  \caption{
    \textbf{Network inference and taxonomic assignment have the highest influence on the inferred network structures.}
    \textbf{(A)} The network constructed using the default pipeline parameters (denosing=dada2, database=ncbi, otu\_filtering=on, network\_inference=sparcc) is compared with networks when one of the steps use a different tool.
    The common connections are in black, connections unique to the network are colored and connections in the default network and but not present in the current network are green.
    \textbf{(B)} The L1 distance of the networks generated by changing one step of the default pipeline against the network generated using the default parameters.
  }
  \label{fig:figure1}
\end{figure}

@@

\setcounter{figure}{0}
\renewcommand{\thefigure}{S\arabic{figure}}

@@

\begin{figure}[h]
  \centering
  \includegraphics[width=0.8\linewidth]{figures2.pdf}
  \caption{Results of the mock community analysis. (A) Weighted unifrac (B) Unweighted unifrac}
  \label{fig:figures2}
\end{figure}

\begin{figure}[h]
  \centering
  \includegraphics[width=0.8\linewidth]{figures3.pdf}
  \caption{Results of the synthetic community analysis. (A) Weighted unifrac (B) Unweighted unifrac}
  \label{fig:figures3}
\end{figure}

\begin{figure}[h]
  \centering
  \includegraphics[width=0.8\linewidth]{pdf/all_denoise_reg.pdf}
  \caption{All pairwise correlations comparing the similarity between different denoising and clustering methods}
  \label{fig:figures4}
\end{figure}

\begin{figure}[h]
  \centering
  \includegraphics[width=\linewidth]{figures4.pdf}
  \caption{
    \textbf{(A)} Taxonomy composition of the 20 most abundant genera predicted using different taxonomy references databases: Greengenes, SILVA and NCBI.
    The legend shows the common and the unique genera among the taxonomy assignments.
}
  \label{fig:figures4}
\end{figure}

\begin{figure}[h]
  \centering
  \includegraphics[width=\linewidth]{figures5.pdf}
  \caption{
    The bray-curtis dissmilarity between the expected taxonomic composition and generated taxonomic composiion for the synthetic datasets.
}
  \label{fig:figures4}
\end{figure}

\begin{figure}[h]
  \centering
  \includegraphics[width=\linewidth]{figures6.pdf}
  \caption{
    The effect of OTU processing measurs on the OTU table
}
  \label{fig:figures4}
\end{figure}
